---
title: "rddj-template"
subtitle: "My analysis"
author: "My Name"
date: "`r Sys.Date()`"
format:
  html:
    code-fold: show
    highlight-style: pygments
    theme: paper
    df-print: kable
    toc: true
    toc-depth: 4
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| echo: false
# CONFIG
user_name <- "fernandomillanvillalobos" # your Git username (only needed if
# you want to deploy to GH pages)
project_name <- "rddj-template" # adapt!
r_version <- "4.2.0" # R-Version to use
options(Ncpus = 4) # use 4 cores for parallelized installation of packages
if (r_version != paste0(version$major, ".", version$minor)) {
  stop("ERROR: specified R version does not match currently used.")
}
```

# Notes

This report was generated on `r Sys.time()`. R version: `r paste0(version$major, ".", version$minor)` on `r version$platform`. Package versions used for this report are pinned in the project's `renv.lock` file, so the exact same versions can always be restored with `renv::restore()`.

...

## R-Script & data

The preprocessing and analysis of the data was conducted in the [R project for statistical computing](https://www.r-project.org/). The Quarto document used to generate this page, and all the resulting data, can be downloaded from [the GitHub repository](https://github.com/`r user_name`/`r project_name`) (see below). Rendering `analysis/main.qmd` reproduces the herein described process and regenerates this page. In the course of this, data from the folder `analysis/input` will be processed and results will be written to `analysis/output`. The published version of this analysis can be accessed through this [link](https://`r user_name`.github.io/`r project_name`/).

## GitHub

The code for the herein described process can also be freely downloaded from [https://github.com/`r user_name`/`r project_name`](https://github.com/`r user_name`/`r project_name`). 

## License

...

## Data description of output files

#### `abc.csv` (Example)

| Attribute | Type | Description |
|-------|------|-----------------------------------------------------------------------------|
| a | Numeric | ... |
| b | Numeric | ... |
| c | Numeric |  ... |

...

# Set up

This project uses [renv](https://rstudio.github.io/renv/) to pin exact package versions instead of relying on a CRAN snapshot service. If you're cloning this repo for the first time, run `renv::restore()` once (or just render this document, which does it for you) to install the versions recorded in `renv.lock`. If this is a brand-new project with no `renv.lock` yet, run `renv::init()` once instead -- see the README for the full setup and package-update workflow.

```{r}
#| echo: false
detach_all_packages <- function() {
  basic_packages_blank <-  c("stats",
                             "graphics",
                             "grDevices",
                             "utils",
                             "datasets",
                             "methods",
                             "base")
  basic_packages <- paste("package:", basic_packages_blank, sep = "")

  package_list <- search()[
    ifelse(unlist(gregexpr("package:", search())) == 1, TRUE, FALSE)]

  package_list <- setdiff(package_list, basic_packages)

  if (length(package_list) > 0)  for (package in package_list) {
    detach(package, character.only = TRUE, unload = TRUE)
    print(paste("package ", package, " detached", sep = ""))
  }
}

detach_all_packages()

# this allows multiple persons to use the same Quarto document without
# adjusting the working directory by themselves all the time. here::here()
# finds the project root by looking for a .Rproj file (or a .here file)
# and resolves all paths relative to it
if (!requireNamespace("here", quietly = TRUE)) {
  install.packages("here")
}
here::i_am("analysis/main.qmd") # main.qmd lives in analysis/, one level
# below the project root -- update this path if the file ever moves

# suppress scientific notation
options(scipen = 999)

# suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

## Define packages

```{r}
# if you don't need a package, remove it from here (commenting not
# sufficient) -- this vector is also what gets restored/loaded below.
# adding a package? add it here, install.packages() it as usual, then run
# renv::snapshot() to record the new version in renv.lock (see README)
# tidyverse: see https://blog.rstudio.org/2016/09/15/tidyverse-1-0-0/
packages <- c(
  "rstudioapi",
  "tidyverse",
  "tidylog",
  "jsonlite",
  "lintr",
  "rmarkdown",
  "rio",
  "cowplot",
  "extrafont",
  "ggrepel",
  "scales",
  "janitor"
)
```

## Install packages

```{r}
# this project uses renv (https://rstudio.github.io/renv/) instead of
# checkpoint/MRAN to keep an isolated, reproducible package library.
# - brand-new project, no renv.lock yet? run renv::init() once, manually,
#   from the console -- that scans the packages above and records their
#   current versions in renv.lock (commit it, renv/activate.R and
#   renv/settings.json afterwards; renv/library/ stays untracked)
# - cloned a project that already has renv.lock? nothing to do by hand,
#   the line below restores those exact versions into a project-local
#   library automatically, no CRAN snapshot server required
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

if (file.exists(here::here("renv.lock"))) {
  # renv doesn't know about here()'s root -- without an explicit project
  # path it falls back to getwd(), which the render process temporarily
  # points at the folder containing this .qmd (analysis/) while chunks
  # run, not the true project root. pass here::here() explicitly so it
  # checks the right place regardless of the current working directory
  renv::restore(project = here::here(), prompt = FALSE)
} else {
  message(
    "No renv.lock found yet -- this looks like a brand-new project.\n",
    "Open the project via its .Rproj file and run renv::init() once from ",
    "the console (not from inside a render), then commit renv.lock, ",
    "renv/activate.R, renv/settings.json and .Rprofile. Re-render afterwards."
  )
}
```

## Load packages

```{r}
invisible(lapply(packages, library, character.only = TRUE))
sessionInfo()
```

## Load additional scripts

```{r}
# if you want to outsource logic to other script files, see README for 
# further information
# Load all visualizations functions as separate scripts -- add/remove
# filenames here rather than adding more read_chunk()/source() pairs below
viz_scripts <- c(
  "dviz.supp.R",
  "themes.R",
  "plot_grid.R",
  "align_legend.R",
  "label_log10.R",
  "outliers.R"
)

invisible(lapply(viz_scripts, function(f) {
  knitr::read_chunk(here::here("analysis", "scripts", f))
  source(here::here("analysis", "scripts", f))
}))
```

# Introduction
# Data Importing
# Data Pre-Processing
# Exploratory Data Analysis (EDA)
## Data Summarization
## Data Visualization

# Linting

The code in this Quarto document is linted with the [lintr package](https://github.com/jimhester/lintr), which is based on the  [tidyverse style guide](http://style.tidyverse.org/). 

```{r}
#| results: hide
# lintr::lint(here::here("analysis", "main.qmd"), linters =
#               lintr::with_defaults(
#                 commented_code_linter = NULL,
#                 trailing_whitespace_linter = NULL
#                 )
#             )
# if you have additional scripts and want them to be linted too, add them here
# lintr::lint(here::here("analysis", "scripts", "my_script.R"))
```
